### 2020-04-06 draft_ABP.tex
Updates from Overleaf

For each element $ I\in \mathcal B$, we define $I^{(0)}=\{I\}$ and  $I^{(1)}$ as the set of all $J\supsetneq I $ such that  $I$ is the ``maximal subset'' of $J$ in $\mathcal{B}$ (that is, there is no $K\in \mathcal{B}$ such that $I\subsetneq K\subsetneq J $). Then, we recursively define 
\begin{equation}
   I^{(i+1)} = \{I^{(i)}_{a}\cup I^{(i)}_{b}\vert I_{a,b}^{(i)}\in I^{(i)},\text{$I_{a}^{(i)}$ and $I_{b}^{(i)}$ are ``maximal subsets'' of $I^{(i)}_{a}\cup I^{(i)}_{b}$ }\}
\end{equation} 
and stop when $\lvert I^{(s)}\rvert =1$. With the defination of $I^{(i)}$, the coresponding $u$-variable is
\begin{equation}
   u_{I} =\prod_{i}(-1)^{i} \prod_{I_{a}^{(i)}\in I^{(i)}} p(I_{a}^{(i)})
\end{equation}

@@

For a generic generalized permutohedra $\mathscr P$, it's usually difficult to solve $S_I$ by $\{F_I\}$  from eq.\eqref{GPfacet} and then get $u$-variables in terms of $\{x_I\}$, but we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which gives us many algebraic equations of $u$-variables. In fact,
\[
\prod_{I\in \mathscr P}x_I^{S_I}=\prod_{J\in \mathscr P}u_J^{F_J}=\prod_{J\in\mathscr P}\prod_{I\subset J,I\in \mathscr P}u_J^{S_I}=\prod_{I\in\mathscr P}\biggl(\prod_{J\supset I,J\in\mathscr P}u_J\bigg)^{S_I},
\]
so
\[
x_I=\prod_{J\supset I,J\in\mathscr P}u_J
\]
for any $I\in \mathscr P$, where we introduce a fake $u$-variable 
$u_{[0,n]}:=x_{[0,n]}$. We know some algebraic equations of $\{x_I\}$, 
for example, linear equations $x_I+x_J=x_{I\cup J}$ for $I\cap J=\varnothing$, 
so (I will omit all $\text{sth}\in \mathscr P$ for convenience.)
\begin{equation*}
	\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=\prod_{K\supset I\cup J}u_K
\end{equation*}
or equivalently
\begin{equation}
\prod_{I\subset K,K\not\supset I\cup J}u_K +
\prod_{J\subset K,K\not\supset I\cup J}u_K = 1.
\end{equation}
({\bf Zhenjie}: I conjecture that all possible $u$-equations are consequences of 
some algebraic equations of $x_I$ which is in fact we have seen in 
the calculation of $1-u_I$. For example, the nonlinear equation (although it's
the consequence of linear equations)
\[
	x_0x_{012}+x_1x_2=x_{01}x_{02}
\]
tells us the $u$-equation of $u_0$ of 2d permutohedron $\mathscr P_2$. Therefore,
another related conjecture is that the variety generated by $u$-equations 
is the one generated by eq.(\theequation) for all disjoint $I$, $J\in \mathscr P$ 
in $u$-space. Can we prove that generalized permutohedra are binary geometries in
this way?
)

For permutohedron $\mathscr P_n$, I conjecture that
\[
1-u_I=1-\prod_{J\supset I}x_J^{(-1)^{|J|-|I|}}=\frac{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J-\prod_{|J|-|I| \text{ even}; J\supset I}x_J}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J}
=\frac{f_{I,n}\prod_{i\not\in I}x_i}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J},
\]
where $f_{I,n}$ is an irreducible polynomial with positive coefficients. It's easy to see $x_i$ for $i\not\in I$ is a factor of numerator by setting $x_i=0$, but it's not obvious whether $f_{I,n}$ is irreducible. I've checked many examples, and corresponding polynomials $f_{I,n}$ are always irreducible.

From
\[
\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
\quad\text{and}\quad
\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
=
\prod_{J\supset I}u_J^{2^{|J|-|I|-1}},
\]
then
\[
\prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supset I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
\]
Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's naturally to conjecture that
\[
1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
\]
where $g$ is a polynomial.
The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers. It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$. Thus, the final conjecture is about the compatibility degree:
\[
(I||J)=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  (I||J)=0 \text{ for $I\subset J$}.
\]
It's not symmetric when $|I|\neq |J|$.

>>>>

For each element $ I\in \mathcal B$, we define $I^{(0)}=\{I\}$ and  $I^{(1)}$ as the set of all $J\supsetneq I $ such that  $I$ is the ``maximal subset'' of $J$ in $\mathcal{B}$ (that is, there is no $K\in \mathcal{B}$ such that $I\subsetneq K\subsetneq J $). Then, we recursively define 
\begin{equation}
   I^{(i+1)} = \{I^{(i)}_{a}\cup I^{(i)}_{b}\vert I_{a,b}^{(i)}\in I^{(i)},\text{$I_{a}^{(i)}$ and $I_{b}^{(i)}$ are ``maximal subsets'' of $I^{(i)}_{a}\cup I^{(i)}_{b}$ }\}
\end{equation} 
and stop when $\lvert I^{(s)}\rvert =1$. With the defination of $I^{(i)}$, the coresponding $u$-variable is
\begin{equation}
   u_{I} =\prod_{i}\prod_{I_{a}^{(i)}\in I^{(i)}} p(I_{a}^{(i)})^{(-1)^{i} }
\end{equation}

@@

For a generic generalized permutohedra $\mathscr P$, it's usually difficult to solve $S_I$ by $\{F_I\}$  from eq.\eqref{GPfacet} and then get $u$-variables in terms of $\{x_I\}$, but we can directly use eq.\eqref{GPfacet} to express $x_I$ by $\{u_I\}$ which gives us many algebraic equations of $u$-variables. In fact,
\[
\prod_{I\in \mathscr P}x_I^{S_I}=\prod_{J\in \mathscr P}u_J^{F_J}=\prod_{J\in\mathscr P}\prod_{I\subset J,I\in \mathscr P}u_J^{S_I}=\prod_{I\in\mathscr P}\biggl(\prod_{J\supset I,J\in\mathscr P}u_J\bigg)^{S_I},
\]
so
\begin{equation}
x_I=\prod_{J\supset I,J\in\mathscr P}u_J
\end{equation}
for any $I\in \mathscr P$, where we introduce a fake $u$-variable 
$u_{[0,n]}:=x_{[0,n]}$. We know some algebraic equations of $\{x_I\}$, 
for example, linear equations $x_I+x_J=x_{I\cup J}$ for $I\cap J=\varnothing$, 
so (I will omit all $\text{sth}\in \mathscr P$ for convenience.)
\begin{equation*}
	\prod_{K\supset I}u_K+\prod_{K\supset J}u_K=\prod_{K\supset I\cup J}u_K
\end{equation*}
or equivalently
\begin{equation}
\prod_{I\subset K,K\not\supset I\cup J}u_K +
\prod_{J\subset K,K\not\supset I\cup J}u_K = 1.
\end{equation}
({\bf Zhenjie}: I conjecture that all possible $u$-equations are consequences of 
some algebraic equations of $x_I$ which is in fact we have seen in 
the calculation of $1-u_I$. For example, the nonlinear equation (although it's
the consequence of linear equations)
\[
	x_0x_{012}+x_1x_2=x_{01}x_{02}
\]
tells us the $u$-equation of $u_0$ of 2d permutohedron $\mathscr P_2$. Therefore,
another related conjecture is that the variety generated by $u$-equations 
is the one generated by eq.(\theequation) for all disjoint $I$, $J\in \mathscr P$ 
in $u$-space. Can we prove that generalized permutohedra are binary geometries in
this way?
)

For permutohedron $\mathscr P_n$, I conjecture that
\[
1-u_I=1-\prod_{J\supset I}x_J^{(-1)^{|J|-|I|}}=\frac{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J-\prod_{|J|-|I| \text{ even}; J\supset I}x_J}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J}
=\frac{f_{I,n}\prod_{i\not\in I}x_i}{\prod_{|J|-|I| \text{ odd}; J\supset I}x_J},
\]
where $f_{I,n}$ is an irreducible polynomial with positive coefficients. It's easy to see $x_i$ for $i\not\in I$ is a factor of the numerator by setting $x_i=0$, but it's not obvious whether $f_{I,n}$ is irreducible. I've checked many examples, and corresponding polynomials $f_{I,n}$ are always irreducible.

From
\[
\prod_{i\not\in I}x_i=\prod_J u_J^{|J|-|I\cap J|}
\quad\text{and}\quad
\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
=
\prod_{J\supset I}u_J^{2^{|J|-|I|-1}},
\]
then
\[
\prod_{i\not\in I}x_i\bigg/\prod_{|J|-|I| \text{ odd}; J\supset I}x_J
=\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}\prod_{J\supset I} u_J^{|J|-|I|-2^{|J|-|I|-1}}.
\]
Since $|J|-|I|-2^{|J|-|I|-1}\leq 0$, it's natural to conjecture that
\begin{equation}
1-u_I=g(u)\prod_{J\not\supset I} u_J^{|J|-|I\cap J|},
\end{equation}
where $g$ is a polynomial.
The product $\prod_{J\not\supset I} u_J^{|J|-|I\cap J|}$ has appeared in all known examples with right powers. It's clear that any compatible $u_J$ for $J\subset I$ doesn't appear in the product because $I\cap J=J$. Thus, the final conjecture is about the compatibility degree:
\[
(I||J)=|J|-|I\cap J|\text{ for $I\not\subset J$},\quad  (I||J)=0 \text{ for $I\subset J$}.
\]
It's not symmetric when $|I|\neq |J|$.
